Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-06-19 sec_results.tex
Updates from Overleaf
updates

 Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the high multiplicity class (0--0.1\%). The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$.
 %The associated yield per trigger particle is compared with the CMS results.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class. The distributions in upper panels are measured with 0--100\% multiplicity class. The distribution in lower panels are measured with 0-0.1\% multiplicity class. Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively. }
	\label{fig:PlotDeltaPhi}
\end{figure}

The spectra of the ridge yield are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared with the CMS results~\cite{Khachatryan:2015lva}. The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$. Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%. Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity, the measurements are can be considered comparable with each other, which insists that measurements of azimuthal correlations can be achieved with ALICE. The spectrum is also compared with model predictions. $\pythiam$ and $\pythiashoving$ are used for the prediction. $\pythiam$ is shown with a black line and predicts no ridge effect in pp collisions, which is expected because the model does not implement any constraint to describe the ridge effect. $\pythiashoving$ shown with a red line describes the effect better than $\pythiam$, however, its yield decreases more rapidly than the data as $\pttrigassoc$ increases.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.99\textwidth]{./figures/Fig1_RidgeYield.pdf} }
	\caption{ The spectra of ridge yield as function of transverse momentum. The filled circles denote the measurement with ALICE and compared with CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open box. The two lines show model predictions from $\pythiam$ (black line) and $\pythiashoving$ (red line). }
	\label{fig:PlotYSpect}
\end{figure}

>>>>

 Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class(0--100\%) and the high multiplicity class (0--0.1\%). The near-side($\Delta\varphi\sim 0$) peak in the minimum bias class is rarely seen in the various transverse momentum range. The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high multiplicity class. The measurements in the high multiplicity class are compared with the CMS results. The near-side peak measured with CMS shows agreement with ALICE measurement, while showing higher yield in the away-side($\Delta\varphi\sim\pi$) peak. The model predictions are represented for the measurements in the high multiplicity class. The $\pythiashoving$ nicely estimates the near-side peak and overestimates the away-side yield fir the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$. The $\pythiashoving$ does not reproduce the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range. $\pythiam$ does not show any peaks in the near-side, which is expected. While not reproducing the near-side peak, $\pythiam$ estimates the away-side peak, which mainly come from the jet--balancing jet correlations.

 %The associated yield per trigger particle is compared with the CMS results.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.99\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class. The distributions in upper panels are measured with 0--100\% multiplicity class. The distribution in lower panels are measured with 0-0.1\% multiplicity class. Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively. The model predictions are presented as colored lines. Blue line corresponds to the $\pythiashoving$ and orange line corresponds to the $\pythiam$}
	\label{fig:PlotDeltaPhi}
\end{figure}

The spectra of the ridge yield are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared with the CMS results~\cite{Khachatryan:2015lva}. The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$. Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%. Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity, the measurements are can be considered comparable with each other, which insists that measurements of azimuthal correlations can be achieved with ALICE. The spectrum is also compared with model predictions. $\pythiam$ and $\pythiashoving$ are used for the prediction. $\pythiam$ is shown with a orange line and predicts no ridge effect in pp collisions, which is expected because the model does not implement any constraint to describe the ridge effect. $\pythiashoving$ shown with a blue line describes the effect better than $\pythiam$, however, its yield decreases more rapidly than the data as $\pttrigassoc$ increases.

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.89\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
	\caption{ The spectra of ridge yield as function of transverse momentum. The filled circles denote the measurement with ALICE and compared with CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box. The two lines show model predictions from $\pythiam$ (orange line) and $\pythiashoving$ (blue line). }
	\label{fig:PlotYSpect}
\end{figure}
